---
title: "Organizing team"
knitr:
  opts_chunk: 
    echo: false
    message: false
    warning: false
---
```{css echo=FALSE}
.card-header-chairs{
  background-color: #FDC08666;
  font-weight: bold;
}
.card-header-team{
  background-color: #BEAED47A;
  font-weight: bold;
}
.cards-display{
  display: grid;
}
```


```{r}
source(here::here("R/functions-team.R"))

team_raw <- yaml::read_yaml("team.yml", readLines.warn = FALSE)

chairs_list <- team_raw[[1]] |> 
  extract_people()  |> 
  dplyr::group_split(name_complete)

organizers_list <- team_raw[[3]] |>
  extract_people() |> 
  dplyr::group_split(name_complete)

```


## About us

On October 25, 2017, an announcement was made by Heather Turner on the R User Group (RUG) Organizers Slack: the R Foundation Conference Committee was interested in the emergence of academic-focused R events in regions not currently covered by useR! In less than a week, we had organized our first videoconference to start thinking about how to face the challenge. This quick response was not the result of mere luck, but the consequence of a year in which the R community — through its local RUGs and social media presence— grew stronger in South America. By mid November everything was set up: a name, a place, a date, and a motivated international organizing committee. The first edition took place in Buenos Aires, Argentina and the second in Santiago de Chile, Chile. This year, the latinamerican R community will meet up in Montevideo, Uruguay.

### LatinR Chairs

```{r}
bslib::layout_column_wrap(class = "cards-display",
  width = 1 / 2,
  gap = "0.5cm",
  height = 100,
  generate_card(chairs_list[[1]], class_group =  "card-header-chairs"),
  generate_card(chairs_list[[2]], class_group =  "card-header-chairs"),
  generate_card(chairs_list[[3]], class_group =  "card-header-chairs")
  
)
```


### Scientific Committee

To be announced!

### Organizer Committee

```{r}
bslib::layout_column_wrap(
  class = "cards-display",
  width = 1 / 2,
  gap = "0.5cm",
  height = 100,
  generate_card(organizers_list[[1]]),
  generate_card(organizers_list[[2]]),
  generate_card(organizers_list[[3]]),
  generate_card(organizers_list[[4]]),
  generate_card(organizers_list[[5]]),
  generate_card(organizers_list[[6]]),
  generate_card(organizers_list[[7]]),
  generate_card(organizers_list[[8]]),
  generate_card(organizers_list[[9]]),
  generate_card(organizers_list[[10]]),
  generate_card(organizers_list[[11]]),
  generate_card(organizers_list[[12]]),
  generate_card(organizers_list[[13]]),
  generate_card(organizers_list[[14]]),
  generate_card(organizers_list[[15]]),
  generate_card(organizers_list[[16]])
)
```


<!-- font awesome -->

```{=html}
<script src="https://kit.fontawesome.com/1f72d6921a.js" crossorigin="anonymous"></script>
```
<!-- font awesome -->
